The limits of self commitment and private paternalism \thanks{}

### 2022-03-10 OA.tex
Learning by not doing analysis & replace eff_cost_loan with APR

\begin{figure}[H]
        \caption{FC as \% of loan - treatment effect}
    \label{fc_pro_2_115}
    \begin{center}
        \centering
        \includegraphics[width=0.50\textwidth]{Figuras/fc_te_115_pro_2.pdf}
    \end{center}
     \scriptsize This figure is the same as in Figure \ref{fc_pro2} Panel (a), but with the subsample restricted to the first 115 days.
     %\textit{Do file: }  \texttt{fc\_te\_115.do}
\end{figure}

\begin{figure}[H]
        \caption{Financial cost effect: charging all fees}
    \label{fc_allfee}
    \begin{center}
        \centering
        \includegraphics[width=0.50\textwidth]{Figuras/fc_allfee_quantile_pro_2.pdf}
    \end{center}
    \scriptsize
     This figure is the analogous to Figure \ref{fc_pro2}(b), except that for the fee-forcing contract we pretend that all clients incurred in their late fees, and therefore inflate the financial cost by summing those fees. This is intended as a kind of worse case scenario for the financial cost of the fee-forcing contract. The circles indicate the quantile treatment effects, while the cross is the (OLS) mean. We still find that the financial cost of will be smaller under the fee-forcing contract in spite of artificially inflating it.
     %\texttt{fc\_all\_fee.do}
\end{figure}

\begin{figure}[H]
        \caption{FC as \% of loan - treatment effect}
    \label{fc_perc}
    \begin{center}
        \centering
        \includegraphics[width=0.50\textwidth]{Figuras/fc_perc_te_allarms.pdf}
    \end{center}
     \scriptsize This figure shows the estimated treatment effect of all arms against the status quo, but normalizing the dependent variable by the value of the loan.
     %\textit{Do file: }  \texttt{fc\_perc\_allarms.do}
\end{figure}

@@

\begin{figure}[H]
        \caption{Empirical CDF of Financial Cost: fee-focing vs status-quo}
    \label{ecdf_fc}
    \begin{center}
        \centering
        \includegraphics[width=0.65\textwidth]{Figuras/cdf_eff_pro_2.pdf}
    \end{center}
    \scriptsize This figure plots the empirical cumulative distribution of financial cost. It does this separately for the fee-forcing contract and for the status-quo contract. The doted line at the bottom is the difference of the status-quo CDF minus the fee-forcing CDF. It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line), and therefore that the former first-order stochastically dominates the later for weakly decreasing utility functions; see Proposition \ref{eq_fosd}.
    % \texttt{ecdf\_fc.do}}
\end{figure}

@@

\vspace{.3in}
\begin{figure}[H]
        \caption{Honest causal tree for the fee forcing contract heterogenous treatment effects}
    \label{casual_tree}
    \begin{center}
        \centering
        \includegraphics[width=.8\textwidth]{Figuras/crf_pro_2_fc_admin_disc.pdf}
    \end{center}
    \footnotesize 
    This is one(it is chosen such that it minimizes the pruned cost, that is it is the tree with the smallest root-node impurity) of the honest causal trees in the random forest we use for the estimation of the heterogeneous treatment effect of the fee-forcing contract. It is meant only as an example of how these trees look like. The forest was such that there are as many estimated treatment effects as there are clients.
     %\footnotesize{ \textit{RScript: }  \texttt{grf.R}
\end{figure}

@@

\begin{figure}[H]
    \caption{Heterogeneous Treatment Effect: Fee-forcing contract}
    \label{HTE_fee_forcing}
    \begin{center}
    %\begin{subfigure}{0.4\textwidth}
    %    \caption{Financial cost}
    %    \centering
    %    \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
    %\end{subfigure}
    \begin{subfigure}{0.7\textwidth}
        \caption{Determinants of effects}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_2.pdf}
    \end{subfigure}

    %\begin{subfigure}{0.4\textwidth}
    %    \caption{Losing Pawn}
    %    \centering
    %    \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
    %\end{subfigure}
    %\begin{subfigure}{0.4\textwidth}
    %    \caption*{}
    %    \centering
    %    \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_2.pdf}
    %\end{subfigure}
    \end{center}
     \scriptsize  This figure estimates bivariate regressions of the estimated client-level heterogeneous treatment effects against the respective covariate from the baseline survey  $\widehat{hte_i} = \alpha + \beta \: X_i + \epsilon_i$. The regressors $X_i$ include (e.g if the family asks for money, if they have savings, if they are overconfident using the definition the text, etc. See this Appendix for a transcription of the survey).
      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
\end{figure}

@@

\begin{figure}[H]
    \caption{Determinants of treatment effects and probability of choosing commitment}
    \label{determinants_ps_hte}
    \begin{center}
    \begin{subfigure}{0.475\textwidth}
        \caption{Determinants of HTE}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_eff_cost_loan_pro_2.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Determinants of propensity score}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/ps_int_vertical_pr_gbc_1.pdf}
    \end{subfigure}

@@

\begin{figure}[H]
    \caption{Treatment effects pooling all arms}
    \label{pooled_arms_te}
    \begin{center}
    \begin{subfigure}{0.45\textwidth}
        \caption{Financial Cost}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_allarms_fc_admin_disc.pdf}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \caption{Lost Pawn}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_allarms_def_c.pdf}
    \end{subfigure}
    \end{center}
     \scriptsize
      %\footnotesize{ \textit{Do file: }  \texttt{te\_allarms.do}}
\end{figure}

>>>>

% \begin{figure}[H]
%         \caption{FC restricted to 115 days}
%     \label{fc_pro_2_115}
%     \begin{center}
%         \centering
%         \includegraphics[width=0.50\textwidth]{Figuras/fc_te_115_pro_2.pdf}
%     \end{center}
%      \scriptsize This figure is the same as in Figure \ref{fc_pro2} Panel (a), but with the subsample restricted to the first 115 days.
%      %\textit{Do file: }  \texttt{fc\_te\_115.do}
% \end{figure}

% \begin{figure}[H]
%         \caption{Financial cost effect: charging all fees}
%     \label{fc_allfee}
%     \begin{center}
%         \centering
%         \includegraphics[width=0.50\textwidth]{Figuras/fc_allfee_quantile_pro_2.pdf}
%     \end{center}
%     \scriptsize
%      This figure is the analogous to Figure \ref{fc_pro2}(b), except that for the fee-forcing contract we pretend that all clients incurred in their late fees, and therefore inflate the financial cost by summing those fees. This is intended as a kind of worse case scenario for the financial cost of the fee-forcing contract. The circles indicate the quantile treatment effects, while the cross is the (OLS) mean. We still find that the financial cost of will be smaller under the fee-forcing contract in spite of artificially inflating it.
%      %\texttt{fc\_all\_fee.do}
% \end{figure}

% \begin{figure}[H]
%         \caption{FC as \% of loan - treatment effect}
%     \label{fc_perc}
%     \begin{center}
%         \centering
%         \includegraphics[width=0.50\textwidth]{Figuras/fc_perc_te_allarms.pdf}
%     \end{center}
%      \scriptsize This figure shows the estimated treatment effect of all arms against the status quo, but normalizing the dependent variable by the value of the loan.
%      %\textit{Do file: }  \texttt{fc\_perc\_allarms.do}
% \end{figure}

@@

\begin{figure}[H]
        \caption{Empirical CDF of APR: fee-focing vs status-quo}
    \label{ecdf_fc}
    \begin{center}
        \centering
        \includegraphics[width=0.65\textwidth]{Figuras/cdf_eff_pro_2.pdf}
    \end{center}
    \scriptsize This figure plots the empirical cumulative distribution of financial cost. It does this separately for the fee-forcing contract and for the status-quo contract. The doted line at the bottom is the difference of the status-quo CDF minus the fee-forcing CDF. It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line), and therefore that the former first-order stochastically dominates the later for weakly decreasing utility functions; see Proposition \ref{eq_fosd}.
    % \texttt{ecdf\_fc.do}}
\end{figure}

@@

\vspace{.3in}
\begin{figure}[H]
        \caption{Honest causal tree for the Forced-commitment contract heterogeneous treatment effects}
    \label{casual_tree}
    \begin{center}
        \centering
        \includegraphics[width=\textwidth]{Figuras/crf_pro_2_apr.pdf}
    \end{center}
    \footnotesize 
    This is one(it is chosen such that it minimizes the pruned cost, that is it is the tree with the smallest root-node impurity) of the honest causal trees in the random forest we use for the estimation of the heterogeneous treatment effect of the fee-forcing contract. It is meant only as an example of how these trees look like. The forest was such that there are as many estimated treatment effects as there are clients.
     %\footnotesize{ \textit{RScript: }  \texttt{grf.R}
\end{figure}

@@

\begin{figure}[H]
        \caption{Single causal tree for the Forced-commitment contract heterogeneous treatment effects}
    \label{casual_tree}
    \begin{center}
        \centering
        \includegraphics[width=\textwidth]{Figuras/ct_pro_2_apr.pdf}
    \end{center}
    \footnotesize

     %\footnotesize{ \textit{RScript: }  \texttt{grf.R}
\end{figure}

% \begin{figure}[H]
%     \caption{Heterogeneous Treatment Effect: Fee-forcing contract}
%     \label{HTE_fee_forcing}
%     \begin{center}
%     %\begin{subfigure}{0.4\textwidth}
%     %    \caption{Financial cost}
%     %    \centering
%     %    \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
%     %\end{subfigure}
%     \begin{subfigure}{0.7\textwidth}
%         \caption{Determinants of effects}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_2.pdf}
%     \end{subfigure}

%     %\begin{subfigure}{0.4\textwidth}
%     %    \caption{Losing Pawn}
%     %    \centering
%     %    \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
%     %\end{subfigure}
%     %\begin{subfigure}{0.4\textwidth}
%     %    \caption*{}
%     %    \centering
%     %    \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_2.pdf}
%     %\end{subfigure}
%     \end{center}
%      \scriptsize  This figure estimates bivariate regressions of the estimated client-level heterogeneous treatment effects against the respective covariate from the baseline survey  $\widehat{hte_i} = \alpha + \beta \: X_i + \epsilon_i$. The regressors $X_i$ include (e.g if the family asks for money, if they have savings, if they are overconfident using the definition the text, etc. See this Appendix for a transcription of the survey).
%       %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
% \end{figure}

@@

\begin{figure}[H]
    \caption{Determinants of treatment effects and probability of choosing commitment}
    \label{determinants_ps_hte}
    \begin{center}
    \begin{subfigure}{0.475\textwidth}
        \caption{Determinants of HTE}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_apr_pro_2.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Determinants of propensity score}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/ps_int_vertical_pr_gbc_1.pdf}
    \end{subfigure}

@@

% \begin{figure}[H]
%     \caption{Treatment effects pooling all arms}
%     \label{pooled_arms_te}
%     \begin{center}
%     \begin{subfigure}{0.45\textwidth}
%         \caption{Financial Cost}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/te_allarms_fc_admin_disc.pdf}
%     \end{subfigure}
%     \begin{subfigure}{0.45\textwidth}
%         \caption{Lost Pawn}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/te_allarms_def_c.pdf}
%     \end{subfigure}
%     \end{center}
%      \scriptsize
%       %\footnotesize{ \textit{Do file: }  \texttt{te\_allarms.do}}
% \end{figure}

### 2022-03-10 donde.tex
Learning by not doing analysis & replace eff_cost_loan with APR

What explains the persistence of a contract so contrary to borrowers’ interests?  First, we show substantial levels of over-optimism among borrowers.  Those most likely to benefit from the commitment contract and \textit{not} choose it are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan.  Second, the existence of commitment-style repayment contracts in pawnshop lending is novel in Mexico.  While forcing individuals into commitment does not cause them to demand it in subsequent loans, \textcolor{red}{in Table \ref{iv_pf}} we show observational evidence of `learning by not doing’:  individuals offered commitment who elect not to take it and subsequently default \textit{do} learn about the benefits of commitment, demanding commitment loans at higher rates on subsequent pawn contracts when given the choice.  Finally, while we are working with a lender who has a social mission and is interested in understanding how to help borrowers, there is no free lunch.  The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.

@@

Figure \ref{main_te} gives the  effect sizes (in standard deviations) of the two main study arms for three outcomes:  default, the financial cost of the loan, and the effective interest rate paid to acquire the borrowed capital.  Very clearly, the Forced arm is significant for all three outcomes, with very substantial treatment effects in magnitudes for default and APR, and the commitment arm is never significant.\footnote{The slight increase in APR for the Choice arm seen in this picture arises from the fact that the APR calculation has the arm-specific loan size in the denominator, and the loans in the Choice arm turn out to be slightly larger on average than the Control.}    In other words, voluntary commitment is ineffective but the use of forced commitment saves the average borrower an amount of money almost twice the APR of a normal US credit card loan.

There are other intermediate outcomes that are impacted by being assigned to frequent payments. Table \ref{mechanisms} shows that the first payment happens 8 days earlier (column 1) in the Forced Commitment arm than in the status quo one, and that the number of payments increases by 0.19 (column 2).% Figure \ref{induced_to_pay_early} in the correlates HTE on financing cost with the HTE time of first payment and shows that those induced to pay earlier are also those that have larger induced reduction in financial cost. 
Treatment effects are concentrated on the intensive margin, as treatment does \textit{not} affect the fraction of clients who pay a positive amount (column 6). The percentage of the loan paid increases by 8 percentage points on average (column 7). However the percentage of the loan paid is not larger for those that end up losing the pawn (first row of column 8).  This last point is critical; this intervention has the potential to do financial harm if it caused individuals to make more payments on loans for which they would end up defaulting.  This result shows that instead what the Forced arm does is allow individuals who would have made partial payment and defaulted to instead recover their pawn.

@@

Another way to push the analysis towards a consideration of borrower welfare is the conjecture that if clients exposed to the installment contract like it, they will be more likely to come back vis-a-vis those that got status quo contract.\footnote{\cite{Laibson2018} hypothesizes that consumers use ``experienced utility'' as a guide to make future purchases in this way.} This is indeed what we find in the data.  We consider this outcome in Table \ref{repeat_loans}.  We can first ask whether the individual ever takes a loan after the initial study loan, an analysis which is simply experimental.  The results show that the Choice arm is no more likely to pawn again, which the Forced arm is X\% more likely to take a second loan.  While this appears to be \texit{prima facie} evidence of greater satisfaction with the lender, interpretation here is complicated by the fact that they were so much more likely to have recovered their pawn and hence to be able to pawn it again.  We can explore this possibility in a number of ways.  First, we can consider the probability that the borrower ever takes another loan using a \textit{different} pawn, an outcome that if anything would be biased downward in the Forced arm.  Finally, we can conduct an endogenous sample split and examine the treatment effects within the sample that does, and does not, recover their pawn from the first loan.  Results indicate that . . .

@@

We view this result as strong evidence that after experiencing the contract demand for it increases, consistent with \cite{Alcohol}'s conjecture that demand for commitment increases with experience with it. However there is an alternative explanation for this result, namely that forcing frequent payments effectively means awarding a smaller loan, and thus that clients may pawn again to compensate for the smaller loan. We are skeptical about this interpretation for several reasons. %First, typically the emergencies that trigger a pawn are short lived (e.g. needing to go to the hospital), and it is unclear why clients in the frequent payment arm wait for several months to re-pawn -- there is no effect of the monthly payment contract on repeat pawning in the first 30 or 60 days of the contract, (see Figure \ref{reincidence_before} in Appendix). 
First,  there are many alternatives lenders in this market, and if they did not like frequent payments why do they come back to Lender $P$ for another loan? Second, the fee is really small at 2\% of 1/3 of the value of the loan. The transaction costs of obtaining another loan are likely larger than incurring in this fee. So if the monthly payment made the current loan ``smaller'' it is probably better to skip the monthly payment and incur in a fee than to get an additional loan. Third, we find larger effects of repeat buying for clients that experienced larger treatment effects, which the alternative explanation cannot explain. Fourth, the effect is present if we condition on clients that recovered their pawn (so it's not driven by pawn recovery). Finally, we were able to obtain observational data for all Lender $P$'s branches for the period January 2016 to May 2020, during which Lender $P$ expanded the new frequent payment contract. Using an instrumental variable strategy that exploits the expansion and availability of the frequent payment contract across branches, we show that being exposed to the frequent payment contract leads to an increase of 50 percentage points in the likelihood that in the subsequent pawn the frequent payment contract is chosen when both the status-quo one and the frequent payment contract are available (see \ref{appendix_b}). This choice cannot be explained by the need of another loan, since it is about \textit{which specific type} of loan the clients chooses conditional on getting one.

@@

In the pawn lending context, however, the results from the two arms of the study that feature `soft' commitment further reinforce the centrality of externally imposed commitment. 
Demand for the Soft Commitment contract  is higher than for the Forced Commitment contract by a factor of 3: {31}\% of clients offered a choice between the status quo contract and the Soft Commitment contract chose commitment.  %Interestingly, the set of people who demand the Soft Commitment contract are different from those that demanded the Forced Commitment one. While in both cases the economically vulnerable demand less, in the case of the Soft Commitment those that we classify as present biased, those that report that they frequently fall into temptation buying, and those that ask for reminders of payment are \textit{less} likely to demand the Soft Commitment contract.  This suggests that those taking up the promise commitment are not the ones needing the commitment (see Figure \ref{interactions_takeup} in the Appendix). 
Nonetheless, we find Soft Commitment, whether chosen or induced, to be completely ineffective in this environment.  Table \ref{impact_soft} and  Figure \ref{fc_pro5}(a) finds that assigning clients to the choice-promise condition has a zero effect on financial cost on average (circles). We see no difference even for the endogenous group that \textit{chose} to promise (squares). This null effect happens not only on average, but also by percentiles (not shown in Figure). There is also no effect on pawn recovery on (first coefficient in Figure \ref{fc_pro5}(b)), even for those that themselves choose to promise. And the null effect carries over if we use the definition of recovery in less than 120 days, or for the (endogenous) subgroups that paid a positive amount. Finally, there is no effect on repeat pawning (Figure \ref{reincidence}).

@@

$$ToT = \frac{\beta^C}{p}; \hspace{15} TuT = \frac{(\beta^F - \beta^C)}{(1-p)}; \hspace{15} (ToT-TuT) = \frac{\beta^C}{p}- \frac{(\beta^F - \beta^C)}{(1-p)}. $$

@@

\textcolor{red}{Discussion to be fortified with updated table}

@@

\begin{table}[H]
\caption{Gains for choosers versus gains from non-choosers (ToT \& TuT)}
\label{tot_tut}
\begin{center}
\scriptsize{\input{./Tables/tot_tut_iv.tex}}
\end{center}
 \scriptsize This table shows estimates of the ToT and the TuT with an IV-LATE framework. The ToT (columns (1)-(3)) is computed as the usual LATE with one-sided non-compliance between the choice and control arm, and the TuT (columns (4)-(6)) is the LATE on non-compliers. Columns (6) and (7) estimates the effect of the compliers on the estimated HTE calculated with the Causal Random Forest. 
%\textit{Do file: } \texttt{tot\_tut\_reg.do}
\end{table}

@@

\begin{figure}[H]
     \caption{Heterogeneous Treatment Effects}
    \label{heterogeneous_effects}
    \begin{center}
    \begin{subfigure}{.45\textwidth}
      \caption{Financial cost (in MXN)}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_pro_2.pdf}
    \end{subfigure}
     \begin{subfigure}{0.45\textwidth}
    \caption{Effective APR}
       \centering
      \includegraphics[width=\textwidth]{Figuras/he_dist_eff_cost_loan_pro_2.pdf}
    \end{subfigure}
     \begin{subfigure}{0.45\textwidth}
    \caption{Default}
       \centering
      \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
    \end{subfigure}    
    \end{center}
         \scriptsize
     plots the distribution of the heterogeneous treatment effects on financial cost, estimated using \cite{atheygrf}.
      %\footnotesize{ } \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}
\end{figure}

>>>>

What explains the persistence of a contract so contrary to borrowers’ interests?  First, we show substantial levels of over-optimism among borrowers.  Those most likely to benefit from the commitment contract and \textit{not} choose it are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan.  Second, the existence of commitment-style repayment contracts in pawnshop lending is novel in Mexico.  While forcing individuals into commitment does not cause them to demand it in subsequent loans, \textcolor{red}{in Table \ref{iv_pf}} we show observational evidence of `learning by not doing’:  individuals offered commitment who elect not to take it \textcolor{red}{and subsequently default} \textit{do} learn about the benefits of commitment, demanding commitment loans at higher rates on subsequent pawn contracts when given the choice.  Finally, while we are working with a lender who has a social mission and is interested in understanding how to help borrowers, there is no free lunch.  The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.

@@

Figure \ref{main_te} gives the  effect sizes (in standard deviations) of the two main study arms for three outcomes:  default, the financial cost of the loan, and the effective interest rate paid to acquire the borrowed capital.  Very clearly, the Forced arm is significant for all three outcomes, with very substantial treatment effects in magnitudes for default and APR, and the commitment arm is never significant.\footnote{The slight increase in APR for the Choice arm seen in this picture arises from the fact that the APR calculation has the arm-specific loan size in the denominator, and the loans in the Choice arm turn out to be slightly smaller (although statistically equal) on average than the Control.}    In other words, voluntary commitment is ineffective but the use of forced commitment saves the average borrower an amount of money almost twice the APR of a normal US credit card loan.

There are other intermediate outcomes that are impacted by being assigned to frequent payments. Table \ref{mechanisms} shows that the first payment happens 8 days earlier (column 1) in the Forced Commitment arm than in the status quo one, and that the number of payments increases by 0.19 (column 4). Treatment effects are concentrated on the intensive margin, as treatment does \textit{not} affect the fraction of clients who pay nothing (column 12). The percentage of the loan paid increases by 9 percentage points on average (column 9). Moreover, the percentage of the loan paid is even smaller for those that end up losing the pawn (first row of column 9). This last point is critical; this intervention has the potential to do financial harm if it caused individuals to make more payments on loans for which they would end up defaulting.  This result shows that instead what the Forced arm does is allow individuals who would have made partial payment and defaulted to instead recover their pawn.

@@

Another way to push the analysis towards a consideration of borrower welfare is the conjecture that if clients exposed to the installment contract like it, they will be more likely to come back vis-a-vis those that got status quo contract.\footnote{\cite{Laibson2018} hypothesizes that consumers use ``experienced utility'' as a guide to make future purchases in this way.} This is indeed what we find in the data.  We consider this outcome in Table \ref{repeat_loans}.  We can first ask whether the individual ever takes a loan after the initial study loan, an analysis which is simply experimental.  The results show that the Choice arm is no more likely to pawn again, which the Forced arm is X\% more likely to take a second loan.  While this appears to be \textit{prima facie} evidence of greater satisfaction with the lender, interpretation here is complicated by the fact that they were so much more likely to have recovered their pawn and hence to be able to pawn it again.  We can explore this possibility in a number of ways.  First, we can consider the probability that the borrower ever takes another loan using a \textit{different} pawn, an outcome that if anything would be biased downward in the Forced arm.  Finally, we can conduct an endogenous sample split and examine the treatment effects within the sample that does, and does not, recover their pawn from the first loan.  Results indicate that . . .

@@

We view this result as strong evidence that after experiencing the contract demand for it increases, consistent with \cite{Alcohol}'s conjecture that demand for commitment increases with experience with it. However there is an alternative explanation for this result, namely that forcing frequent payments effectively means awarding a smaller loan, and thus that clients may pawn again to compensate for the smaller loan. We are skeptical about this interpretation for several reasons. %First, typically the emergencies that trigger a pawn are short lived (e.g. needing to go to the hospital), and it is unclear why clients in the frequent payment arm wait for several months to re-pawn -- there is no effect of the monthly payment contract on repeat pawning in the first 30 or 60 days of the contract, (see Figure \ref{reincidence_before} in Appendix). 
First,  there are many alternative lenders in this market, and if they did not like frequent payments why do they come back to Lender $P$ for another loan? Second, the fee is really small at 2\% of 1/3 of the value of the loan. The transaction costs of obtaining another loan are likely larger than incurring in this fee. So if the monthly payment made the current loan ``smaller'' it is probably better to skip the monthly payment and incur in a fee than to get an additional loan. Third, we find larger effects of repeat buying for clients that experienced larger treatment effects, which the alternative explanation cannot explain. Fourth, the effect is present if we condition on clients that recovered their pawn (so it's not driven by pawn recovery). Finally, we were able to obtain observational data for all Lender $P$'s branches for the period January 2016 to May 2020, during which Lender $P$ expanded the new frequent payment contract. Using an instrumental variable strategy that exploits the expansion and availability of the frequent payment contract across branches, we show that being exposed to the frequent payment contract leads to an increase of 50 percentage points in the likelihood that in the subsequent pawn the frequent payment contract is chosen when both the status-quo one and the frequent payment contract are available (see \ref{appendix_b}). This choice cannot be explained by the need of another loan, since it is about \textit{which specific type} of loan the clients chooses conditional on getting one.

@@

In the pawn lending context, however, the results from the two arms of the study that feature `soft' commitment further reinforce the centrality of externally imposed commitment. 
Demand for the Soft Commitment contract  is higher than for the Forced Commitment contract by a factor of 3: {31}\% of clients offered a choice between the status quo contract and the Soft Commitment contract chose commitment.  %Interestingly, the set of people who demand the Soft Commitment contract are different from those that demanded the Forced Commitment one. While in both cases the economically vulnerable demand less, in the case of the Soft Commitment those that we classify as present biased, those that report that they frequently fall into temptation buying, and those that ask for reminders of payment are \textit{less} likely to demand the Soft Commitment contract.  This suggests that those taking up the promise commitment are not the ones needing the commitment (see Figure \ref{interactions_takeup} in the Appendix). 
Nonetheless, we find Soft Commitment, whether chosen or induced, to be completely ineffective in this environment.  Table \ref{impact_soft} and  Figure \ref{effect_promises} finds that assigning clients to the choice-promise condition has a zero effect on financial cost, recovery, and the effective APR on average (Panel (a)). We see no difference even for the endogenous group that \textit{chose} to promise. This null effect happens not only on average, but also by percentiles (Figure \ref{qreg_chooser_nonchooser}, panels (c) \& (d)).
% There is also no effect on pawn recovery on (first coefficient in Figure \ref{fc_pro5}(b)), even for those that themselves choose to promise. And the null effect carries over if we use the definition of recovery in less than 120 days, or for the (endogenous) subgroups that paid a positive amount. Finally, there is no effect on repeat pawning (Figure \ref{reincidence}).

@@

\[ToT = \frac{\beta^C}{p}; \hspace{15} TuT = \frac{(\beta^F - \beta^C)}{(1-p)}; \hspace{15} (ToT-TuT) = \frac{\beta^C}{p}- \frac{(\beta^F - \beta^C)}{(1-p)}. \]

@@

\textcolor{red}{Discussion to be fortified with updated table}\ref{tot_tut}

@@

\begin{table}[H]
\caption{Gains for choosers versus gains from non-choosers (ToT \& TuT)}
\label{tot_tut}
\begin{center}
\scriptsize{\input{./Tables/tot_tut_reg.tex}}
\end{center}
 \scriptsize This table shows estimates of the ToT and the TuT with an IV-LATE framework. The ToT is computed as the usual LATE with one-sided non-compliance between the choice and control arm, and the TuT is the LATE on non-compliers. 
%\textit{Do file: } \texttt{tot\_tut\_reg.do}
\end{table}

\begin{table}[H]
\caption{Learning analysis with experimental data}
\label{learning_reg}
\begin{center}
\scriptsize{\input{./Tables/learning_exp.tex}}
\end{center}
 \scriptsize This table shows choice after experience of an experimental arm in the previous loan. Columns (1)-(4) restrict the sample to borrowers whose second loan falls in the Choice commitment arm. Dependent variable in columns (5)-(8) is `ever chooses commitment', a dummy variable defined to be $0$ if borrower didn't take a loan, or if borrower took a loan and didn't choose commitment, and it is $1$ only when borrower took a loan and chose commitment. 
%\textit{Do file: } \texttt{learning\_reg.do}
\end{table}

\begin{table}[H]
\caption{Differential attrition}
\label{diff_att}
\begin{center}
\scriptsize{\input{./Tables/differential_attrition.tex}}
\end{center}
 \scriptsize This table shows differential attrition in the experimental arms for (1) experiencing a second arm and (2) when the second loan is a Choice commitment arm.
%\textit{Do file: } \texttt{learning\_reg.do}
\end{table}

@@

\begin{figure}[H]
     \caption{Heterogeneous Treatment Effects}
    \label{heterogeneous_effects}
    \begin{center}
    \begin{subfigure}{.45\textwidth}
      \caption{Financial cost (in MXN)}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_pro_2.pdf}
    \end{subfigure}
     \begin{subfigure}{0.45\textwidth}
    \caption{Effective APR}
       \centering
      \includegraphics[width=\textwidth]{Figuras/he_dist_apr_pro_2.pdf}
    \end{subfigure}
     \begin{subfigure}{0.45\textwidth}
    \caption{Default}
       \centering
      \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
    \end{subfigure}    
    \end{center}
         \scriptsize
     plots the distribution of the heterogeneous treatment effects on financial cost, estimated using \cite{atheygrf}.
      %\footnotesize{ } \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}
\end{figure}
